---
title: "Lab 0 - Hello R!"
author: "Arthur Herman"
date: "1/17/23"
format: pdf
editor: visual
---

## Load Packages

```{r}
#| label: load-packages
#| message: false
library(tidyverse)
library(datasauRus)
```

## Exercise 1

There are 3 variables - dataset, x, and y. There are also 1,846 rows and 3 columns

## Exercise 2

```{r}
#| label: plot-dino
#| fig-height: 5
#| fig-width: 5
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) + 
  geom_point()
```

```{r}
#| label: cor-dino
#| fig-height: 5
#| fig-width: 5
dino_data %>%
  summarize(r = cor(x, y))
```

## Exercise 3

```{r}
#| label: plot-circle
#| fig-height: 5
#| fig-width: 5
circle_data <- datasaurus_dozen |>
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Some more narrative can go here.

```{r}
#| label: cor-circle
#| fig-height: 5
#| fig-width: 5
circle_data |>
     summarize(r = cor(x, y))
```

Both are very not correlated and non-linear

## Exercise 4

```{r}
#| fig-height: 5
#| fig-width: 5
star_data <- datasaurus_dozen |>
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r}
#| fig-height: 5
#| fig-width: 5
star_data |>
  summarize(r = cor(x, y))
```

the r value remains very similar, although it is a bit smaller for the star than the r for the dino.

## Exercise 5

```{r}
#| fig-height: 10
#| fig-width: 6
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")

```

```{r}
#| fig-height: 10
#| fig-width: 6
datasaurus_dozen |>
  group_by(dataset) |>
  summarize(r = cor(x, y))
```

I notice that although the plots appear significantly varied, the r values contain only slight differences. It is interesting to contrast the plots versus the correlated r-values because physically there are only slight similarities between the plots in regards to the correlation between the x and y coordinates, yet when represented by r-values, these are only shown as slight changes.
